---
title: "lab8"
author: "Marco Palombo"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(corrplot)
library(broom)
library(here)
library(modelsummary)
```
## read in sol_homes.csv

```{r}
homes <- read_csv(here("data", "slo_homes.csv"))
```

### Create a subset with foru cities, called homes_subset
only homes from:
san luis obispo
atascadero
AG
santa maria

```{r}
homes_subset <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))
```

create a summary table that has the mean and standard deviation of home prices grouped by city and sale status

```{r, include = FALSE, eval = FALSE}
homes_subset %>% 
  group_by(City, Status) %>% 
  summarize(average = mean(Price), 
            dev = sd(Price),
            mean_sqft = mean(SqFt))

```

```{r}
# explore relationship between squarefootage and price
ggplot(data = homes_subset, aes(y = Price, x = SqFt))+
geom_point()+
  geom_smooth(method = lm)

```

### Try a few linear methods
Use multiple linear regresion to investigaterealtionships between several predictor variables and home price.

Creat 2 different permutations of model
1: price as function of: city, bedrooms, bathrooms, quare footage, status
2: price as function of city sqftm status
```{r}
model1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt+ Status, data = homes_subset)
summary(model1)


model2 <- lm(Price ~ City + SqFt + Status, data = homes_subset)
summary(model2)

model3 <- lm(Price ~ City + Bedrooms + SqFt + Status, data = homes_subset)
summary(model3)

```

### Explore correlations between quntative values

make subset called homes_quant(strtin grom home_subset) that only contains the variables from price through sqFT

```{r}
homes_quant <- homes_subset %>% 
  select(Price:SqFt)

homes_cor <- cor(homes_quant)
corrplot(homes_cor)
```

```{r}
#com[are aic values
AIC(model1)
AIC(model2)
```

### Use modelsummary() to return multiple model outputs

```{r}

modelsummary(list(model1, model2, model3))
```

```{r}
# diagnostic plots for lm1
plot(model1)
```

```{r}
#use broom::augment() to return ther prediction s for existing observations
home_predictions <- augment(model1)
```

```{r}
ggplot(data =home_predictions, aes(x = .resid))+
geom_histogram()
```

